The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-27 article.tex
Put the CDK version discussed in this paper in a variable for quick changing/reference.

@@

  In previous versions of the API, stereochemistry was represented disparately hindering 
  interconversion between and within file formats. In CDK 1.5.x the core representation 
  has been standardized upon and procedures updated or added to enable duplicate checking,
  pattern matching, and interconversion.

@@

CDK \textbf{2.0} adds support for V3000 and has optimized and extended
support for V2000. Currently these are considered separate formats requiring
a user to know what version is being read beforehand. Future APIs will aim
to simplify this and provide a unified reader. An overview of currently
supported CTfile formats is given in Table~2\ref{tab:ctfileFormats}.

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds~\cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure~8\label{fig:sgroups}). CDK \textbf{2.0} adds 
supports for representation, reading, writing, and depiction.

>>>>

\def \cdkversion {\textbf{2.0}}

@@

  In previous versions of the API, stereochemistry was represented disparately hindering 
  interconversion between and within file formats. In CDK \cdkversion{} the core representation 
  has been standardized upon and procedures updated or added to enable duplicate checking,
  pattern matching, and interconversion.

@@

CDK \cdkversion{} adds support for V3000 and has optimized and extended
support for V2000. Currently these are considered separate formats requiring
a user to know what version is being read beforehand. Future APIs will aim
to simplify this and provide a unified reader. An overview of currently
supported CTfile formats is given in Table~2\ref{tab:ctfileFormats}.

CTfile Sgroups capture and organise high level information about sets of atoms
and bonds~\cite{Gushurst91}. There are four types of Sgroup: Display Shortcuts, Polymers,
Mixtures, and Data. The most familiar Sgroups from an end user perspective are structure 
repeat units (e.g. bracketing) and abbreviations (Figure~8\label{fig:sgroups}). CDK \cdkversion{} adds 
supports for representation, reading, writing, and depiction.
